A comprehensive analysis of natural sequence variation within the <i>Arabidopsis

### 2018-07-14 manuscript/03-AFBs.Rmd
correctly render AFB section as html

(fig:AFB_structure_vars) A TIR1 structure (2P1Q) in gold, with residues 
```{r AFB_structure_vars, fig.cap='(fig:AFB_structure_vars)'}
knitr::include_graphics()
```

>>>>

(fig:AFB_structure_vars) A TIR1 structure (2P1Q) in gold, with residues 
```{r AFB_structure_vars, fig.cap='(fig:AFB_structure_vars)'}
#knitr::include_graphics()
```

### 2018-07-14 manuscript/index.Rmd
correctly render AFB section as html

output:
  word_document:
    toc: yes
  html_document:
    fig_caption: yes
    toc: yes
always_allow_html: yes
fontfamily: Helvetica
fontsize: 11pt

@@

#devtools::install_github("wrightrc/r1001genomes", ref = "auxin-natural-variation")
library(ape)
library(r1001genomes)
library(DT)
library(tidyverse)
library(magrittr)
library(RColorBrewer)
library(ggpmisc)
library(ggthemes)
library(ggseqlogo)
library(ggtree)
library(reticulate)
library(scales)
library(viridis)
library(ips)
library(knitr)

>>>>

@@

#devtools::install_github("wrightrc/r1001genomes", ref = "auxin-natural-variation")
library(ape)
library(r1001genomes)
library(DT)
library(tidyverse)
library(magrittr)
library(RColorBrewer)
library(ggpmisc)
library(ggthemes)
library(ggseqlogo)
library(ggtree)
library(reticulate)
library(scales)
library(viridis)
library(ips)
library(knitr)
library(dplyr)
